---
title: "Agriculture_Endusers"
output: html_document
---




```{r}
# Install
install.packages("tm")  # for text mining
install.packages("SnowballC") # for text stemming
install.packages("wordcloud") # word-cloud generator 
install.packages("RColorBrewer") # color palettes
install.packages("ggmosaic")

```




# Load the required libraries
```{r}
library(haven)
library(labelled)
library(ggplot2)
library(dplyr)
library(tidytext)
library("RColorBrewer")
library(tidyr)
library("tm")
library("SnowballC")
library("wordcloud")
library(tidyverse)
```


# Import the spss file into R
```{r}
Agr_spss <- read_sav("C:/Users/bbosa/OneDrive/Documents/Data_Visualisation/Categorical_Data_Visualisation/Data/Final EndUser/AgricUser.sav")
```

# To explore the spss file
```{r}
look_for(Agr_spss)
```

```{r}
glimpse(Agr_spss)
```



# Explore the dataset
```{r}

names(Agr_spss)
```



```{r}
# Rename variables

names(Agr_spss)[17:21] <- c(
  "N350 million counterpart fund–RAAMP",
  "Establishment of OYSADA",
  "Construction of the OYSADA Headquarters, Saki",
  "N106,850,000 Agriculture Credit Facilities\nto 658 peasant farmers",
  "Accelerated Agricultural Development Scheme")

names(Agr_spss)[22:31] <- c("Fertilizer","Seeds/stems","Insecticide","Pesticide","Farm Extension services","Mechanized Equipment","Access to markets","Agric Credit","Road and rail infrastructure","Land clearing")


names(Agr_spss)[34:43] <- c(
  "Fertilizer_","Seeds/stems_","Insecticide_","Pesticide_","Farm Extension services_","Mechanized Equipment_","Access to markets_","Agric Credit_","Road and rail infrastructure_","Land clearing_")
```


# Indentify the Variables in the Data file
```{r}
names(Agr_spss)
```

# Remove the unnecessary variables
```{r}
Agr_spss <- Agr_spss[,-c(1:3, 6:11)]
```


# To drop unused labels and coerce all variables to factors for anlysis purposes
```{r}
Agr_spss <- Agr_spss %>% unlabelled(drop_unused_labels = TRUE)
pillar::glimpse(Agr_spss)
```

# Explore the data through Visualisations
## Bar chart
```{r}

ggplot(Agr_spss, aes(x = LGA1)) + geom_bar(aes(fill = STATUS))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

# Explore the data through Visualisations
## Bar chart
```{r}

ggplot(Agr_spss, aes(x = Zone)) + geom_bar(aes(fill = AGE_GROUP))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


# Explore the data through Visualisations
## Bar chart
```{r}

ggplot(Agr_spss, aes(x = AGE_GROUP)) + geom_bar(aes(fill = SEX))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Bar Chart 2
```{r}

ggplot(Agr_spss, aes(y =LGA1)) +
geom_bar(aes(fill = STATUS),
position = "fill")+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  scale_x_continuous(labels=scales::percent)
```


```{r}

df <- Agr_spss %>% 
group_by(STATUS,AGE_GROUP,SEX) %>%
summarise(counts =n())


ggplot(df, aes(
  y = reorder_within(STATUS, counts, SEX),
  x = counts, fill= SEX)) +
  geom_bar(stat = "identity") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  geom_text(aes(label=counts), 
            vjust = 0.5, hjust = 0.4)+
  facet_grid(SEX ~ AGE_GROUP , scales = "free",
             labeller = label_value)+
             scale_y_reordered()+
 ylab("STATUS") +
  xlab("Number of Respondents")+
  labs(fill = "GENDER")
```



## Bar chart 9
```{r}

names(Agr_spss)

Agr_spsst <- Agr_spss %>% pivot_longer(
  cols = "N350 million counterpart fund–RAAMP":"Accelerated Agricultural Development Scheme",
  names_to = "interventions",
  values_to = "opinion") %>% 
   filter(opinion != "I Don't know")

Agr_spsst$opinion <- droplevels(Agr_spsst$opinion)


Agr_spsstt <- Agr_spsst %>% 
group_by(interventions,opinion)%>% 
summarise(counts =n()) %>% 
  mutate(pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

ggplot(Agr_spsstt, aes(x =  Agr_spsstt$interventions,
                       y = Agr_spsstt$pct, fill = opinion)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(Agr_spsstt$pct,accuracy = 0.1L),
            size = 6, 
            fontface = "bold",
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "How effective are these interventions in the\nAgriculture sector by the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Intervention", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```



```{r}

Agr_spssh <- Agr_spsst %>% 
  filter(interventions %in% c( "N106,850,000 Agriculture Credit Facilities\nto 658 peasant farmers")) %>% 
  group_by(interventions,opinion)%>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))


levels(Agr_spssh$opinion)

ggplot(Agr_spssh, aes(x =  Agr_spssh$interventions,
                       y = Agr_spssh$pct, fill = opinion)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "How effective are these interventions in the\nAgriculture sector by the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
 scale_fill_brewer(palette="Set2")+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```


```{r}
Agr_spssw <- Agr_spsst %>% 
  filter(interventions %in% c( 
    "Accelerated Agricultural Development Scheme",                      
    "N350 million counterpart fund–RAAMP",
    "Establishment of OYSADA")) %>% 
  group_by(interventions,opinion)%>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))


levels(Agr_spssh$opinion)

ggplot(Agr_spssw, aes(x =  Agr_spssw$interventions,
                       y = Agr_spssw$pct, fill = opinion)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "How effective are these interventions in the\nAgriculture sector by the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
 scale_fill_brewer(palette="Set2")+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```


```{r}
names(Agr_spss)

Agr_spssa <- Agr_spss %>% pivot_longer(
  cols = "Fertilizer":"Land clearing",
  names_to = "Inputs",
  values_to = "opinion") %>% 
   filter(opinion != "Don't Know")

levels(Agr_spssa$opinion)

Agr_spssa$opinion <- droplevels(Agr_spssa$opinion)

levels(Agr_spssa$opinion)

Agr_spssat <- Agr_spssa %>% 
group_by(Inputs,opinion)%>% 
summarise(counts =n()) %>% 
  mutate(pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

ggplot(Agr_spssat, aes(x =  Agr_spssat$Inputs,
                       y = Agr_spssat$pct, fill = opinion)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(Agr_spssat$pct,accuracy = 0.1L),
            size = 6, 
            fontface = "bold",
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Which of the following agricultural inputs/services\n are accessible to you under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Inputs/Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```


```{r}
Agr_spssa$Zone

Agr_spsswf <- Agr_spssa %>% 
  filter(Inputs %in% 
           c( "Fertilizer",
              "Seeds/stems",
              "Pesticide",
              "Farm Extension services",
              "Mechanized Equipment", 
              "Agric Credit",
              "Road and rail infrastructure" ,
              "Land clearing")) %>% 
  group_by(Inputs,opinion) %>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct)) %>% 
  filter(!Zone %in% 
           c("Oke Ogun 1",
             "Ibadan Main City",
             "Oke Ogun 2",
             "Oyo"))


ggplot(Agr_spsswf, aes(x =  Agr_spsswf$Inputs,
                       y = Agr_spsswf$pct, fill = opinion)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
  theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Which of the following agricultural inputs/services\n are accessible to you under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Inputs/Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```


```{r}
Agr_spssa$Inputs

Agr_spsswfo <- Agr_spssa %>% 
  filter(Inputs %in% c( "Access to markets")) %>% 
  group_by(Inputs,opinion) %>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

ggplot(Agr_spsswfo, aes(x =  Agr_spsswfo$Inputs,
                       y = Agr_spsswfo$pct, fill = opinion)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
  theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Which of the following agricultural inputs/services\n are accessible to you under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Inputs/Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```


```{r}
#Using Base R
Agr_spssa <- Agr_spssa %>% 
  filter(opinion != "Don't Know")

 Agr_spssa$opinion <- droplevels(Agr_spssa$opinion)


mosaicplot( ~ Inputs + opinion  , data = Agr_spssa,
           col=brewer.pal(n=2, name = "Set2"),
           las=2,
           main="Are you aware of the existence of \nOyo State Health Insurance Agency?",
           xlab="", 
           ylab="Response",
           cex.axis=1,)
```




```{r}

library(ggmosaic)
 ggplot(data = Agr_spssa) +
  geom_mosaic(aes(x = product(opinion,Inputs), fill=opinion),
               divider=mosaic("v")) +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(title='f(rude_to_recline)') +
    theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold")) +
   labs(title = "Which of the following agricultural inputs/services\n are accessible to you under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Proportion of Respondents", y ="Inputs/Services" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```



```{r}

library(ggmosaic)
 ggplot(data = Agr_spssa) +
  geom_mosaic(aes(x = product(opinion,Inputs), fill=opinion),
               divider=mosaic("v")) +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(title='f(rude_to_recline)') +
    theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold")) +
   labs(title = "Which of the following agricultural inputs/services\n are accessible to you under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Proportion of Respondents", y ="Inputs/Services" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```


```{r}
names(Agr_spss)

Agr_spsso <- Agr_spss %>% pivot_longer(
  cols = c(25:34),
  names_to = "Services",
  values_to = "rating")



Agr_spssco <- Agr_spsso %>% 
  filter(rating != "I don't know") %>% 
group_by(Services,rating)%>% 
summarise(counts =n()) %>% 
  mutate(pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

levels(Agr_spssco$rating)

Agr_spssco$rating <- droplevels(Agr_spssco$rating)

levels(Agr_spssco$rating)

Agr_spssco$rating <- fct_relevel(Agr_spssco$rating, c("Worse", "Unchanged", "Better"))

levels(Agr_spssco$rating)

custom_color <- c('#fc8d62','#969696','#66c2a5')
ggplot(Agr_spssco, aes(x =  Agr_spssco$Services,
                       y = Agr_spssco$pct, fill = rating)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(Agr_spssco$pct,accuracy = 0.1L),
            size = 6, 
            fontface = "bold",
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the last administration, rate the availability\n of farm inputs/services under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_manual(values=custom_color)
```



```{r}
Agr_spsso <- Agr_spss %>% pivot_longer(
  cols = c(25:34),
  names_to = "Services",
  values_to = "rating") %>% 
  filter(rating !="I don't know")

Agr_spsso$rating <- droplevels(Agr_spsso$rating)

levels(Agr_spsso$rating)

Agr_spsscot <- Agr_spsso %>% 
  filter(Services %in% c("Mechanized Equipment",
                         "Farm Extension services_",
                         "Agric Credit_",
                         "Pesticide_",
                         "Land clearing_")) %>% 
group_by(Services,rating)%>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

Agr_spsscot$rating <- fct_relevel(Agr_spsscot$rating, c("Worse", "Unchanged", "Better"))

levels(Agr_spsscot$rating)

custom_color <- c('#fc8d62','#969696','#66c2a5')
ggplot(Agr_spsscot, aes(x =  Agr_spsscot$Services,
                       y = Agr_spsscot$pct, fill = rating)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the last administration, rate the availability\n of farm inputs/services under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_manual(values=custom_color)+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```



```{r}
Agr_spssg <- Agr_spsso %>% 
  filter(Services %in% "Access to markets_") %>% 
group_by(Services,rating)%>% 
  mutate(counts =n(),
    pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))

Agr_spssg$rating <- fct_relevel(Agr_spssg$rating, c("Worse", "Unchanged", "Better"))

levels(Agr_spssg$rating)

custom_color <- c('#fc8d62','#969696','#66c2a5')
ggplot(Agr_spssg, aes(x =  Agr_spssg$Services,
                       y = Agr_spssg$pct, fill = rating)) +
  geom_bar(stat="identity", position ="fill") + 
  coord_flip()+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 14, face = "italic"), 
        plot.caption = element_text(size = 12), 
        text = element_text(family = "Georgia", size = 18, face = "bold"),
        strip.text.y = element_text(angle = 0))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the last administration, rate the availability\n of farm inputs/services under the current administration?", 
       subtitle = "Mid-Term Survey for Agricultural Sector", 
       x = "Services", y ="Proportion of Respondents" , 
       caption =  "N=896 Respondents")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_manual(values=custom_color)+
    facet_grid(Zone ~ .,scales = "free", space = "free") +
  geom_hline(yintercept = 0.50, linetype="dashed", 
                color = "#e7298a", size=1.5)
```


