---
title: "Regulated_Health_Ins"
output: html_document
---
# Set A Working Directory

```{r}
getwd()
```

# Install packages
```{r eval = FALSE}
install.packages("labelled")
install.packages("haven")
install.packages("tidyverse")
install.packages("RColorBrewer")
install.packages("tidyr")
install.packages("tidytext")

```




# Load the required libraries
```{r}
library(haven)
library(labelled)
library(ggplot2)
library(dplyr)
library(tidytext)
library("RColorBrewer")
library(tidyr)
```

# Import the spss file into R
```{r}
hlthrgl_spss <- read_sav("C:/Users/bbosa/OneDrive/Documents/Data_Visualisation/Categorical_Data_Visualisation/Data/AllFinalRegulated/HealthReg.sav")
```


# To explore the spss file
```{r}
look_for(hlthrgl_spss) # Looks for value and variable labels to exlore them
```

## Explore the Structure of the Data file
```{r}
str(hlthrgl_spss) # Detailed structure of the data
```

## Indentify the Variables in the Data file
```{r}
names(hlthrgl_spss)  # or `colnames(hlthrgl_spss)`
```

## To remove unnecessary variable names
```{r}
hlthrgl_spss <- hlthrgl_spss[,-c(1:3, 7:15, 19)]
names(hlthrgl_spss)
```


# To rename variables and put variable labels
```{r}
names(hlthrgl_spss)[1:6]<- c("zn","LGA","city","typ","outpatient","area")
names(hlthrgl_spss)[16] <- "OSHIA"

var_label(hlthrgl_spss[,1:6]) <- c("Zone","Local Government",
                                    "City","Type of Faciity","OutPatient", "Area")

var_label(hlthrgl_spss[16]) <-"Are you aware of the Oyo State Health Insurance Agency?" 

val_labels(hlthrgl_spss[,6]) <- c( rural = 1, urban = 2)

val_labels(hlthrgl_spss[,4]) <- c( Referral_H. = 1, 
                                   Public_PHC = 2, 
                                   Public_SHC = 3,
                                   Private_H. = 4,
                                   Private_Phar. =5 )

```


# Rename variables
```{r}
names(hlthrgl_spss)[7:13] <- c("Cost of Accreditation",
                               "Process of Licencing",
                               "Licence Renewal",
                               "Supervision Effectiveness",
                               "Deployment of Medical Specialists",
                               "Approval and Distribution\n Drugs and Vaccines",
                               "Periodic Supervision of Activities")
```



# To see the class of the variables
```{r}
pillar::glimpse(hlthrgl_spss)
```

# To drop unused labels and coerce all variables to factors for anlysis purposes
```{r}
hlthrgl_spss <- hlthrgl_spss %>% unlabelled(drop_unused_labels = TRUE)
pillar::glimpse(hlthrgl_spss)
```


# Explore the data through Visualisations
## Bar chart
```{r}

ggplot(hlthrgl_spss, aes(x = LGA)) + geom_bar(aes(fill = area))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


## Bar Chart 2
```{r}

ggplot(hlthrgl_spss, aes(y =LGA)) +
geom_bar(aes(fill = area),
position = "fill")+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  scale_x_continuous(labels=scales::percent)


```


## Bar Chart 3
```{r}

df <- hlthrgl_spss %>%
group_by(LGA, area) %>%
summarise(counts =n())


ggplot(df, aes(
x = reorder_within(LGA, counts, area),
y = counts, fill= area)) +
geom_bar(stat = "identity") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
geom_text(aes(label=counts),
vjust = -0.5, hjust = 0.5)+
facet_grid(.~ area , scales = "free",
labeller = label_value)+
scale_x_reordered()+
xlab("Local Government") +
ylab("Number of Respondents")
```

## Bar chat 4
```{r}
ggplot(df, aes(
  y = reorder_within(LGA, counts, area),
  x = counts, fill= area)) +
  geom_bar(stat = "identity") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  geom_text(aes(label=counts), 
            vjust = 0.5, hjust = -0.5)+
  facet_grid(area~ . , scales = "free",
             labeller = label_value)+
             scale_y_reordered()+
 ylab("Local Government") +
  xlab("Number of Respondents")+
  labs(fill = "Area")
```

## Bar chart 5
```{r}

ggplot(hlthrgl_spss, aes(y =typ)) +
geom_bar(aes(fill = outpatient),
position = position_stack(reverse = TRUE))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Bar Chat 6
```{r}


ggplot(hlthrgl_spss, aes(y =typ)) +
geom_bar(aes(fill = outpatient),
position = position_stack(reverse = TRUE))+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Bar Chart 7
```{r}
df1 <- hlthrgl_spss %>%
group_by(typ, outpatient) %>%
summarise(counts =n())%>% 
  mutate(pct = counts/sum(counts),
         lb = cumsum(pct))


ggplot(df1, aes(
y = reorder_within(df1$typ, df1$counts, df1$outpatient),
x = counts, fill= outpatient)) +
geom_bar(stat = "identity", position = "stack") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      legend.position="right",
         legend.direction="vertical",
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"),
      plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
geom_text(aes(label=df1$counts),
vjust = -0.5, hjust = 0.5)+
scale_y_reordered()+
 labs(fill = "Responses",
     title = "Do you offer Outpatient Services only?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       y = "Type of Facility", x ="Number of Respondents" , 
       caption =  "N=117 Regulated Institutions")
```

## Bar Chart 8
```{r}
ggplot(df1, aes(
y = reorder_within(df1$typ, df1$counts, df1$outpatient),
x = counts, fill= df1$outpatient)) +
geom_bar(stat = "identity") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      legend.position="right",
         legend.direction="vertical",
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"),
      plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
geom_text(aes(label=df1$counts),
vjust = -0.5, hjust = 0.5)+
facet_grid(df1$outpatient ~. , scales = "free",
labeller = label_value)+
scale_y_reordered()+
   labs(fill = "Responses",
     title = "Do you offer Outpatient Services only?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       y = "Type of Facility", x ="Number of Respondents" , 
       caption =  "N=117 Regulated Institutions")
```

## Bar chart 9
```{r}
ggplot(data=df1, aes(x=df1$typ, y=df1$pct, fill=outpatient)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(df1$pct,accuracy = 0.1L),
            size = 4, 
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Do you offer Outpatient Services only?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Type of Facility", y ="Proportion of Respondents" , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```

## Mosaic plots
```{r}
#Using Base R


mosaicplot(~zn + OSHIA, data = hlthrgl_spss,
           col=brewer.pal(n=2, name = "Set2"),
           las=2,
           main="Are you aware of the existence of \nOyo State Health Insurance Agency?",
           xlab="", 
           ylab="Response",
           cex.axis=1,)
```


### Mosaic plot 2
```{r}
mosaicplot(~LGA + OSHIA, data = hlthrgl_spss,
           main = "Are you aware of the existence of Oyo State Health Insurance Agency?", 
           sub = NULL, 
           xlab = "", 
           ylab = "Respose",
           col=c("Skyblue","Seagreen1"), 
           las=2, cex.axis = 1.5)
```


### Mosaic Plot 3
```{r}
mosaicplot(~typ + OSHIA, data = hlthrgl_spss,
           main = "Are you aware of the existence of Oyo State Health Insurance Agency?", 
           sub = NULL, 
           xlab = "", 
           ylab = "Respose",
           col=c("Cyan","Pink"), 
           las=2, cex.axis = 1.5)
```


## Bar chart 10
```{r}


hlthrgl_spsst <- hlthrgl_spss %>% pivot_longer(
  cols = "Cost of Accreditation":"Periodic Supervision of Activities",
  names_to = "effect",
  values_to = "opinion")



ggplot(hlthrgl_spsst, aes(y = effect)) +
geom_bar(aes(fill = opinion),position="fill")+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  scale_x_continuous(labels=scales::percent)

```

## Bar chart 11
```{r}
df3 <- hlthrgl_spsst %>% 
group_by(effect,opinion)%>% 
summarise(counts =n()) %>% 
  mutate(pct = (counts)/sum(counts),
         label_ypos=cumsum(pct))



ggplot(data=df3, aes(x=df3$effect, y=df3$pct, fill=opinion)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(df3$pct,accuracy = 0.1L),
            size = 4, 
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "To what extent are you affected by the nOyo state government’s\n Regulatory Activities in the last 2 years?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Activities", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```

## Bar chart 12
```{r}
fill <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df3, aes(x=df3$effect, y=df3$pct, fill=opinion)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(df3$pct,accuracy = 0.1L),
            size = 4, 
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "To what extent are you affected by the  Oyo state government’s\n Regulatory Activities in the last 2 years?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Activities", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=fill)
```


## Bar chart 13
```{r}
df4 <- hlthrgl_spsst  %>% 
 group_by(effect, opinion) %>%
  mutate(counts =n(),
         pct=(counts)/sum(counts),
         label_ypos=cumsum(pct)) %>% 
  ungroup()

custom_color <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df4, aes(x=df4$effect, y=df4$pct, fill=opinion)) +
  geom_bar(stat="identity", position="fill") + 
  coord_flip()+
  facet_grid(typ ~ .)+ 
  theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
    guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "To what extent are you affected by the  Oyo state government’s Regulatory Activities in the last 2 years?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Regulatory Activities", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=custom_color)+
  facet_grid(typ ~ .,scales='free_y')
```

## Bar chart 14
```{r}
  
df5 <- hlthrgl_spsst  %>% 
  group_by(effect, opinion) %>%
  mutate(counts =n(),
         pct=(counts)/sum(counts),
         label_ypos=cumsum(pct)) %>% 
  ungroup()

custom_color <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df5, aes(x=df5$effect, y=df5$pct, fill=opinion)) +
  geom_bar(stat="identity",
           position = "fill") + 
  coord_flip() +
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15),
        panel.border=element_blank(), axis.line=element_line())+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "To what extent are you affected by the  Oyo state government’s Regulatory Activities in the last 2 years?", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Activities", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=custom_color)+
  facet_grid(typ ~ .,scales='free_y')+
  ylim(0.00, 1)


```


```{r}
names(hlthrgl_spsst)[10:14] <- c("Cost of Accreditation",
                               "Process of Licencing and\n Licencing Renewal",
                               "Supervision Effectiveness",
                               "Deployment of Medical Specialists",
                               "Approval and Distribution\n Drugs and Vaccines")

names(hlthrgl_spsst)
```


## Bar chart 15
```{r}

hlthrgl_spsstt <- hlthrgl_spsst %>% pivot_longer(
  cols = "Cost of Accreditation":"Approval and Distribution\n Drugs and Vaccines",
  names_to = "services",
  values_to = "rating")


ggplot(hlthrgl_spsstt, aes(y =services)) +
geom_bar(aes(fill = rating),position="fill")+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  scale_x_continuous(labels=scales::percent)

```

## Bar chart 16
```{r}
df6 <- hlthrgl_spsstt %>% 
group_by(services,rating)%>% 
summarise(counts =n()) %>% 
  mutate(proptn= (counts)/sum(counts),
         cumm_proptn=cumsum(proptn))

ggplot(data=df6, aes(x=df6$services, y=df6$proptn, fill=df6$rating)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(df6$proptn,accuracy = 0.1L),
            size = 4, 
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", 
                                     size = 12, 
                                     face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the past 2 years, Rate the availability of the following services;", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Services", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
  scale_fill_brewer(palette="Set2")
```

## Bar chart 17
```{r}
color_fill <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df6, aes(x=df6$services, y=df6$proptn, fill=df6$rating)) +
  geom_bar(stat="identity") + 
  coord_flip()+
  geom_text(label=scales::percent(df6$proptn,accuracy = 0.1L),
            size = 4, 
            position = position_stack(vjust = 0.5))+
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", 
                                     size = 12, 
                                     face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the past 2 years, Rate the availability of the following services;", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Services", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=color_fill)
```



## Bar chart 18
```{r}
df7 <- hlthrgl_spsstt  %>% 
 group_by(services, rating) %>%
  mutate(counts =n(),
         proptn=(counts)/sum(counts),
         cumm_proptn=cumsum(proptn)) %>% 
  ungroup()

custom_color <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df7, aes(x=df7$services, y=df7$proptn, fill=df7$rating)) +
  geom_bar(stat="identity", position="fill") + 
  coord_flip()+
  facet_grid(typ ~ .)+ 
  theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15))+
    guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the past 2 years, Rate the availability of the following services;", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Services", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=custom_color)+
  facet_grid(typ ~ .,scales='free_y')
```


## Bar chart 19
```{r}
  
df8 <- hlthrgl_spsstt  %>% 
  group_by(services, rating) %>%
  mutate(counts =n(),
          proptn=(counts)/sum(counts),
         cumm_proptn=cumsum(proptn)) %>% 
  ungroup()



custom_color <- c('#66c2a5','#fc8d62','#969696','#e78ac3','#a6d854')
ggplot(data=df8, aes(x=df8$services, y=df8$proptn, fill=df8$rating)) +
  geom_bar(stat="identity",
           position = "fill") + 
  coord_flip() +
   theme(legend.position="top",
         legend.direction="horizontal",
         legend.title = element_blank(),
        plot.subtitle = element_text(color = "gray20", size = 12, face = "italic"), 
        plot.caption = element_text(size = 10), 
        text = element_text(family = "Georgia", size = 15),
        panel.border=element_blank(), axis.line=element_line())+
   guides(fill = guide_legend(reverse=TRUE))+
  labs(title = "Compared to the past 2 years, Rate the availability of the following services;", 
       subtitle = "Mid-Term Survey for Health Regulated Institutions", 
       x = "Services", y =NULL , 
       caption =  "N=117 Regulated Institutions")+
   scale_fill_hue(l=80, c=20)+
scale_fill_manual(values=custom_color)+
  facet_grid(typ ~ .,scales='free_y')+
  ylim(0.00, 1)

```


